Supporting Information

### 2018-04-19 SupportingInformation.Rmd
cause4copula section modified

```{r calculation_phylo_data, echo=F, results="hide"}
source("phylo_dat_fn.R")
phylo_dat<-read.csv("./Data/Anolis/contrasts.csv",header = T)
#class(phylo_dat) #it's a data.frame
#----------------------------------------------------------------------------------------------------
# Generating all copula plots between different pathlength and traits 
pdf("./Results/Anolis_results/contrasts_csv_results/contrasts_csv_pathlength_traits_cop_plot.pdf",width=20, height = 20)
op<-par(mfrow=c(4,4))
i<-1
  for(j in c(1:13)){
    v_phylo<-phylo_dat_fn(data=phylo_dat,i=i,j=j,ploton = T)
    #plot(v_phylo[,1],v_phylo[,2],col="green4")
    #mtext("(i,j)=(",i,", ",j,")")
    mtext(paste0(" [",i,",",j,"] ", ","," n=",dim(v_phylo)[1]),side = 3,col="blue")
  } 
par(op)
dev.off()
#------------------------------------------------------------------------------------------------------------
# Generating all 12 by 12 copula plots between different traits
pdf("./Results/Anolis_results/contrasts_csv_results/contrasts_csv_btw_traits_cop_plot.pdf",width=20, height = 20)
op<-par(mfrow=c(12,12))
for(i in c(2:13)){
  for(j in c(2:13)){
    v_phylo<-phylo_dat_fn(data=phylo_dat,i=i,j=j,ploton = T)
    mtext(paste0(" [",i,",",j,"] ", ","," n=",dim(v_phylo)[1]),side = 3,col="blue")
  } 
}
par(op)
dev.off()
#----------------------------------------------------------------------------------------
# Generating raw data plot btw AVG.humerus and AVG.radius from contrasts.csv
pdf("./Results/Anolis_results/contrasts_csv_results/rawdataplot_AVG_humerus_radius.pdf")
op<-par(mar=c(5.1, 4.1, 0.2, 2.1))
plot(phylo_dat$AVG.humerus,phylo_dat$AVG.radius,type="p",col="red",xlab="AVG.humerus",ylab="AVG.radius",
     cex.lab=1.5,cex.axis=1.5)
par(op)
dev.off()
#--------------------------------------------------------------------------------------------
# Generating copula plot btw AVG.humerus and AVG.radius from contrasts.csv
pdf("./Results/Anolis_results/contrasts_csv_results/copula_AVG_humerus_radius.pdf")
v_contrasts_67<-phylo_dat_fn(data=phylo_dat,i=6,j=7,ploton = T)
dev.off()
```

\begin{figure}[!h]
\textbf{ \hspace{5.5 cm} (A) \hspace{7 cm} (B)  } \\
\begin{center}
\includegraphics[width=3 in]{./Results/Anolis_results/contrasts_csv_results/rawdataplot_AVG_humerus_radius.pdf}
\includegraphics[width=3 in]{./Results/Anolis_results/contrasts_csv_results/copula_AVG_humerus_radius.pdf}
\caption{\textbf{(A)} Plot of the raw AVG.radius vs. AVG.humerus phylogenetic traits. \textbf{(B)} Copula plot of AVG.radius vs. AVG.humerus phylogenetic traits. Obtained by applying ranks separately to each variable, and then dividing the ranks by $n+1$ where $n=`r nrow(v_contrasts_67)`$ is the number of contrasts (see Sec. \ref{Model_selection}). \label{fig_raw_cop_AVG_humerus_radius}}
\end{center}
\end{figure}

@@

```{r bivMS_contrasts_67, echo=F, cache=T, cache.extra=list(seed,v_contrasts_67,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
set.seed(seed)
# Now do Model Selection for [i,j]=[6,7]
# 6 : AVG. humerus
# 7 : AVG. radius
source("OurBiCopSelect.R")
families<-c(1,3:10,13:14,16:20)
BivMS_contrasts_67<-OurBiCopSelect(u1=v_contrasts_67[,1],u2=v_contrasts_67[,2],families=families,
                          level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,
                          gofnormal=F,status=F)
saveRDS(BivMS_contrasts_67,file="./Results/Anolis_results/contrasts_csv_results/BivMS_contrasts_67.RDS")
```

@@

<!--Display model selection results for contrasts data in a table-->
```{r tab_contrasts_67fit, echo=F, results='markup'}
h<-BivMS_contrasts_67$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for contrasts between AVG.humerus and AVG.radius dataset. \\label{tab_contrasts_67fit}",
             booktabs=T)
```

@@

```{r stat_contrasts_67_graphic_approach, echo=F, results="hide", cache=T, cache.extra=list(seed,v_contrasts_67,mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
source("bivfunctionplot.R")
set.seed(seed) 
# Now do NPA for v_contrasts_67
source("bivfunctionplot.R")
stat_contrasts_67_ga<-bivfunctionplot(v=v_contrasts_67,resloc="./Results/Anolis_results/contrasts_csv_results/",
                                      nametag="contrasts_67",numbin = 4)
```

@@

@@

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->
```{r cause4copula, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"))}
source("Cause4copula.R")
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF.pdf", width=12, height=6)
op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

Plotter_Cause4copula_GOF(fcode=3,method = "spearman",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=13,method="spearman",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=4,method = "spearman",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=14,method="spearman",num_keep_last=500,BS=100)

Plotter_Cause4copula_GOF(fcode=3,method = "kendall",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=13,method="kendall",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=4,method = "kendall",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=14,method="kendall",num_keep_last=500,BS=100)

@@

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF.pdf)

>>>>

```{r calculation_phylo_data, echo=F, results="hide"}
source("phylo_dat_fn.R")
phylo_dat<-read.csv("./Data/Anolis/contrasts.csv",header = T)
#class(phylo_dat) #it's a data.frame
# no NA/missing value in this dataset
#----------------------------------------------------------------------------------------------------
# Generating all copula plots between different pathlength and traits 
pdf("./Results/Anolis_results/contrasts_csv_results/contrasts_csv_pathlength_traits_cop_plot.pdf",width=20, height = 20)
op<-par(mfrow=c(4,4))
i<-1
  for(j in c(1:13)){
    v_phylo<-phylo_dat_fn(data=phylo_dat,i=i,j=j,ploton = T)
    mtext(paste0(" [",i,",",j,"] ", ","," n=",dim(v_phylo)[1]),side = 3,col="blue")
  } 
par(op)
dev.off()
#------------------------------------------------------------------------------------------------------------
# Generating all 12 by 12 copula plots between different traits
pdf("./Results/Anolis_results/contrasts_csv_results/contrasts_csv_btw_traits_cop_plot.pdf",width=20, height = 20)
op<-par(mfrow=c(12,12))
for(i in c(2:13)){
  for(j in c(2:13)){
    v_phylo<-phylo_dat_fn(data=phylo_dat,i=i,j=j,ploton = T)
    mtext(paste0(" [",i,",",j,"] ", ","," n=",dim(v_phylo)[1]),side = 4,col="blue",line=0.01)
  } 
}
par(op)
dev.off()
#----------------------------------------------------------------------------------------
# Generating raw data plot btw AVG.ltoe.IV and AVG.humerus from contrasts.csv
pdf("./Results/Anolis_results/contrasts_csv_results/rawdataplot_AVG_ltoe_humerus.pdf")
op<-par(mar=c(5.1, 4.1, 0.2, 2.1))
plot(phylo_dat$AVG.ltoe.IV,phylo_dat$AVG.humerus,type="p",col="red",xlab="AVG.ltoe.IV",ylab="AVG.humerus",
     cex.lab=1.5,cex.axis=1.5)
par(op)
dev.off()
#--------------------------------------------------------------------------------------------
# Generating copula plot btw AVG.ltoe.IV and AVG.humerus from contrasts.csv
pdf("./Results/Anolis_results/contrasts_csv_results/copula_AVG_ltoe_humerus.pdf")
v_contrasts_67<-phylo_dat_fn(data=phylo_dat,i=6,j=7,ploton = T)
dev.off()
```

\begin{figure}[!h]
\textbf{ \hspace{5.5 cm} (A) \hspace{7 cm} (B)  } \\
\begin{center}
\includegraphics[width=3 in]{./Results/Anolis_results/contrasts_csv_results/rawdataplot_AVG_ltoe_humerus.pdf}
\includegraphics[width=3 in]{./Results/Anolis_results/contrasts_csv_results/copula_AVG_ltoe_humerus.pdf}
\caption{\textbf{(A)} Plot of the raw AVG.ltoe.IV vs. AVG.humerus phylogenetic traits. \textbf{(B)} Copula plot of AVG.ltoe.IV vs. AVG.humerus phylogenetic traits. Obtained by applying ranks separately to each variable, and then dividing the ranks by $n+1$ where $n=`r nrow(v_contrasts_67)`$ is the number of contrasts (see Sec. \ref{Model_selection}). \label{fig_raw_cop_AVG_humerus_ltoe}}
\end{center}
\end{figure}

@@

```{r bivMS_contrasts_67, echo=F, cache=T, cache.extra=list(seed,v_contrasts_67,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
set.seed(seed)
# Now do Model Selection for [i,j]=[6,7]
# 6 : AVG. ltoe.IV
# 7 : AVG. humerus
source("OurBiCopSelect.R")
families<-c(1,3:10,13:14,16:20)
BivMS_contrasts_67<-OurBiCopSelect(u1=v_contrasts_67[,1],u2=v_contrasts_67[,2],families=families,
                          level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,
                          gofnormal=F,status=F)
saveRDS(BivMS_contrasts_67,file="./Results/Anolis_results/contrasts_csv_results/BivMS_contrasts_67.RDS")
```

@@

<!--Display model selection results for contrasts data in a table-->
```{r tab_contrasts_67fit, echo=F, results='markup'}
h<-BivMS_contrasts_67$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for contrasts between AVG.ltoe.IV and AVG.humerus dataset. \\label{tab_contrasts_67fit}",
             booktabs=T)
```

@@

```{r stat_contrasts_67_graphic_approach, echo=F, results="hide", cache=T, cache.extra=list(seed,v_contrasts_67,mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
source("bivfunctionplot.R")
set.seed(seed) 
# Now do NPA for v_contrasts_67
stat_contrasts_67_ga<-bivfunctionplot(v=v_contrasts_67,resloc="./Results/Anolis_results/contrasts_csv_results/",
                                      nametag="contrasts_67",numbin = 4)
```

@@

Q1/2: How are copula structure of ecologically influential climate variables changing as part of climate change? We now know the copula structure of environmental variables can induce (sometimes similar but not the same) copula structure in the pops, but we don’t really know how a change in the environment cop structure would make what kind of change in the pop cop structure. How?

@@

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->
```{r cause4copula, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf", width=12, height=6)
op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

Plotter_Cause4copula_GOF(fcode=3,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=13,method="spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=4,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=14,method="spearman",num_keep_last=500,BS=1000)

Plotter_Cause4copula_GOF(fcode=3,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=13,method="kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=4,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(fcode=14,method="kendall",num_keep_last=500,BS=1000)

op2<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise","population", "p_CvM", "p_KS"), col = c("red", "blue", "magenta", "green2"),
       cex = 0.8, pch = c(2, 6, 16, 16), lty = c(1, 1, NA, NA), xpd = TRUE, horiz = TRUE, inset = c(0,0), 
       bty = "n") 
par(op2)
dev.off()
#----------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=12, height=6)
op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

Plotter_Cause4copula_GOF(fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(fcode=13,method="spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(fcode=14,method="spearman",num_keep_last=2500,BS=1000)

Plotter_Cause4copula_GOF(fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(fcode=13,method="kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(fcode=14,method="kendall",num_keep_last=2500,BS=1000)

@@

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last **500** points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf)

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last **2500** points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf)
